Finding GENERAL Defect Prediction Models Within Hundreds of Software Projects

### 2020-03-19 response.tex

\review{(2.15) [Sec. 2.3] “If they ask ‘are we sure XYZ causes problems?’, can we say that we have mined enough projects to ensure that XYZ is problematic?” We can say XYZ is probably problematic, but that doesn’t answer the deeper question about causality. Do you agree?}

\response{You are quite right. Probabilistic data miner results  should never claim causality. We have removed the ambiguous statement and added XYZ is a statistical predictor for bug prone code \citeresp{2-15}.}

@@

% \review{(1.16) [Sec. 2.4] “This art of moving data and/or lessons learned from one project to another is Transfer Learning.” I do not agree with this definition. Please cite this definition or use the definition of transfer learning established by the machine learning community.}

\review{(2.17) [Sec. 2.4] “Successful transfer learning can have two variants…” Cite these variants. This is a software engineering paper—not a machine learning paper—that should reference other work for these fundamental details.}

\response{Thank you for your comment. We indeed forgot to add the citations in the previous manuscript. We have added the citations in this manuscript \citeresp{2-17}.}

@@

\review{(2.18) [Sec. 3.2] “…for large sample datasets…” What is the size of the design matrix? Does 21 product metrics and five process metrics mean 26 columns? If there are 697 projects and snapshots every six months, then how many rows are there?}

\response{Thank you for your comment, the previous manuscript did not included all the details regarding the design matrix. In this manuscript we have included much details regarding the design matrix in \citeresp{2-18}. \fig{meta} shows the distribution of number of rows in each projects, which is a snapshots of the projects from 6 months back of the last commit. We can see from the \fig{meta} median number of rows is around 120 in this group of 697 projects explored.}

\begin{quote}
    \response{Using the   Understand tool~\cite{visualize},
we calculated different variations (i.e. average, max etc.) of 21 product and 5 process metrics, with a total 66 attributes/columns to build defect prediction models
 (see Table~\ref{tbl:metric}).
These product  metrics are calculated from snapshots of the projects from 6 months back of the last commit. The process metrics are computed using the change history in the six-months period before the split date via manual collection of data using scripts.}
\end{quote}

@@

\review{(2.20) [Sec. 4.1] “stratified k=5 fold cross-validation an” Incomplete.}

\response{Thank you for your comment, we have fixed the incomplete sentence. We have also ensured there are no more incomplete sentences in this version.}

\review{(2.21) [Sec. 5] “To put that another way, the answer to ‘is is [sic] possible to learn from too much data’, is ‘depends on what you value’” How does your concept of learning from too much data relate to the concept of overfitting? Same concept? Different concepts? If so, how are they different?}

\response{
Over-fitting is a problem that can occur with data of any size. Over-fitting is a well-studies problem that explores bias/variance trade offs.
But over-fitting is an orthogonal issue to negative
transfer learning.
To clarify all that we have added text to \citeresp{2-21}:}
\begin{quote}
\response{
This sections ask if conclusions always improve as we learn from more and more data.
This can be an issue since if a new project
is fundamentally different to all past projects, then irrelevant ideas from the past will be
inappropriately applied to the present situation. ~\\
This is a special problem that arises when combining old data  with new data.}
\end{quote}

@@

\review{(2.22) [Abstract] “When one exemplar project…offers the best advice then it can be used to offer advice for many other projects.” The word advice is confusing here. The so-called bellwether does not offer advice or recommendations. It is simply used as a characterization, right?}

\response{Thank you for your comment, you are quite correct the use of ``advice or recommendations'' is rather ambiguous in this context. We have changed these references of ``advice or recommendations'' to ``prediction'' in this version of manuscript.}

@@

\review{(2.23) [Sec. 2.3] “…among developers, there is little agreement on what many issues relating to software.” Please reword.}

\response{Thank you for your comment. We have made changes \citeresp{2-23} to the sentence to be understandable }

@@

\review{(2.26) [Sec. 5] Why do you need a figure (Fig. 6) for two numbers?}

\response{Thank you for your comment, the figure Fig. 6 (now Fig~\ref{fig:time}) is important as this figure shows the difference of time taken for each method. XXXXXXX include with updated charts.XXXXXXX}

\section*{Reviewer 3}

\response{Thank you very much for your detailed review.
As we said to the associated editor, the previous draft made the following mistake:
\bi
\item We assumed that the  core motivation for this work
was widely known and accepted in the community. That was a mistake. 
\item
Consequently,this draft completely rewrites the Introduction
to include much more background information on the 
presence of the problem studied here.
\ei
We have made some additional corrections, clarifications, and revisions, as directed by your comments. To assist in your review, we refer to specific locations of each of the changes using \respto{1-XX}.}

\review{(3.1)The manuscript introduces a new approach GENERAL, which just applies hierarchical clustering. As far as I understand, hierarchical clustering is a well-known, standard, and largely-evaluated clustering algorithm. I don’t really see the need to rebrand it with a new name. What is the difference between GENERAL and hierarchical clustering other than the GENERAL is applied to defect prediction?}

\response{Thank you for your comment. We have added detailed notes on how GENERAL and each of its component works. To clarify, GENERAL
does several things, only one of which is a standard
hierarchical clusterer. First, it clusters using the BIRCH clusterer
as a sub-routine. Secondly, it walks over the cluster tree generated
from BIRCH conducting experiments to see what best local model works for a subbranch. As part of those experiments: (2a) it builds models using a data mining on data from a sub-tree; (2b) it compares
different models from sibling trees using a multi-objective domination predicate. Note that this second part is not part of standard BIRCH. For full details on this process, please  \citeresp{3-1}.}

@@

\review{(3.2) Figure 1 “shows a hypothetical cost comparison in AWS between standard bellwether and GENERAL.” If the Figure is hypothetical, why do we need it? Is it based on real data? As far as I understand, the plot is merely speculation and as such is should be included in scientific papers.}

\response{Thank you for your comments.   We have removed all the hypothetical graphs and added data from actual experiment in this version of manuscript.}

\review{(3.3) I am also very concerned about the (unproven) assumption that we can make conclusions that hold across multiple projects. While the dataset includes 700 projects, we have no information about the project, the domain applications, critically (e.g., safety-critical systems vs. generic open-source Java libraries). I don’t really see how a model trained on dozens of open-source apache libraries can be applied to robotics, medical systems, etc. Note that for the latter domains, testing, requirements engineering, and maintenance are different and have peculiar standards (e.g., MC/CD coverage for automotive systems vs. statement coverage for non-critical systems).  }

\response{With respect, we are unclear on this comment. As shown by our precision, recall, false alarm, etc results what this paper
shows is that we can make general conclusions across this space of projects. And, elsewhere, bellwethers have worked to generate
configurations for cloud-based tools~\cite{krishna2019whence},
effort estimation, predicting Github issue close time, and
code bad smell detection~\cite{krishna2018bellwethers,krishna2017simpler, nair19a, krishna16, krishna16a}. So we would characterize bellwethers as method that has been demonstrated useful in many domains. However, and this is the point of this paper, the existing  method does not scale to large data sets. Hence, this paper.}

@@

\review{(3.4) Similar to Figure 1, Figure 2 discussed hypothetical results/comparisons. Why do we need to speculate on hypothetical data rather than real data? The last two paragraphs in Section 2.2 make little sense to me. There is no reason to have them, if not for contributing to the overall overselling.}

\response{Thank you for your comments. In the last draft, Figure 1 and Figure 2 were indeed based on hypothetical data.  We have removed the hypothetical Figure 1 and Figure 2 in this draft.}

@@

\review{(3.5) Up to page 5 (Sections 1-2), the paper broadly discusses the importance of learning models from hundreds of projects to have more generic and more reliable software analytics in a broader sense. However, from Section 3 to Section 6, the manuscript focuses on defect prediction ONLY.}

\response{Thank you for your comment. You are correct. The paper
is now focused on defect prediction (see our new title). }

@@

\review{(3.6) How can we use one single sub-domain (i.e., defect prediction) to make bold statements that should be valid for software analytics in general? This overselling concerns me a lot. This manuscript DOES NOT provide any evidence that GENERAL works and is applicable for other contexts other than defect prediction. In other words, SE is not only Defect Prediction.}

\response{Thank you for your comment. If you are asking ``does bellwether work for multiple domains'', then we would say ``yes'' as shown by Krishna et al.'s TSE and ASE paper~\cite{krishna2018bellwethers,krishna2017simpler, krishna16, krishna16a} (see our comment for 3.3).}

\response{But if you are asking ``are these conclusions general across the space of all projects, we would agree with you that the answer must be ``no''.  The prior draft reached too far on this point. Our new end to the introduction \citeresp{3-6}  makes it clear that we are talking about ``more generalizable to more projects'' rather than ``general to all projects''.}

@@

\review{(3.9) Furthermore, the dataset looks quite strange to me. Looking at the defect distributions (left-most boxplot in Figure 4), I do see that 75\% of the projects (the last quartile) have more than 60\% of defective modules (classes/methods?). Some have a defective percentage above 80\%. Do we need machine learning to predict defects in projects where almost all modules are defectives? In these projects, a simple, constant classifier would work the best. The results also show this for ZeroR in Section 5.}

\response{unclear on this. zeroR tells us that it is not enough to do simple things. Not sure how to answer.XXXX}

\review{(3.10) Throughout the manuscript, the complexity of GENERAL is suggested to be $O(m * (N/m)^2)$. But there is proof about the complexity whatsoever. Either the manuscript cites proofs from existing papers (e.g., related work on hierarchical clustering) or provides a complete proof (perhaps in an appendix).}

\response{Thank you for your comment, we didn't included detailed analysis of complexity of our method in the last manuscript. We have added much details and an step by step analysis \citeresp{3-10} of complexity of the algorithm shown in Fig~\ref{fig:Pseudo-code}.}

@@

\review{(3.11a) All the results are summarized in one single table (Figure 7), which shows the mean and the standard deviation of five evaluation metrics, as well as the rank of the statistical tests. There are two problems in aggregating the data in this way: (1)I am not sure that the arithmetic mean and the standard deviation are the appropriate metrics to use. Are the data normally distributed? Do we have many outliers? Perhaps, median and IQR are more appropriate as they are less affected by outliers.}

\response{Thank you for your comment, you are quite correct. We used arithmetic mean and standard deviation as our metrics to showcase our result in the last manuscript, which may be affected by outliers and skew the results. In this manuscript, we have replaced arithmetic mean and standard deviation with median and IQR in figure~\ref{fig:Statistical}.}

\review{(3.11b)Maybe, the boxplots would be the most appropriate way to show the distributions. (2)The average across 700 projects makes little sense and hides what happens in each project. What happens per project? In how many projects does GENERAL performs better than the standard bellwether learner?}

\response{Thank you for your comments. The Fig~\ref{fig:Statistical} is a form of boxplot, where the black dot represents the median and the spread of the black line represents the 25th and 75th percentile of the data. Also note that the ranks we offer in that figure (in the left-hand-column) are generated via non-parametric statistics
(bootstrap and the A12 effect size test) that do not assume gaususians.}

@@

\review{(3.12) Section 5 contains the following recommendation “As to ZeroR, we cannot recommend that approach. While ZeroR makes few mistakes (low ifas and low pfs), it scores badly on other measures (very low recalls and popt(20).” This argument does not convince me as ZeroR gets the best results for two metrics (as far as I understand). Please elaborate more on why we cannot use ZeroR. Besides, ZeroR may work relatively well because of projects with a very large number of defects. Perhaps, some in-depth analysis of the correlation between defect distributions and performances of the models would be very useful.}

\response{Thank you for your comments, in the last manuscript we did not properly explained why the model ZeroR can not be recommend. We have updated the figure~\ref{fig:Statistical} to replace arithmetic mean and standard deviation with median and IQR. We can see from the figure~\ref{fig:Statistical}, the ZeroR model has a recall and pf of zero with IQR diff between 75th and 25th percentile as 100, which signifies as the model either predicts everything as defective or non-defective it will not be able to predict any defective module at all if the defect ratio is less than 50\%, while for projects with defect ratio is more than 50\% it will predict everything as defective with high false positive.}
